---
title: "Rapa-by-mtDNA Interaction Analysis"
output:
  html_document:
    toc: true
params:
   FDR: 0.05
   LFC: 0.0
date: "2023-06-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
FDR.Thresh <- params$FDR
LFC.Thresh <- params$LFC
set.seed(1234)
```

## Load packages.
This document depends on the following packages:
```{r, message=FALSE}
library(tidyverse)
library(DESeq2)
library(apeglm)
library(eulerr)
library(EnhancedVolcano)
library(flybaseR)
library(drosophila2.db)
library(org.Dm.eg.db)
library(AnnotationDbi)
library(repr)
library(vsn)
library(pheatmap)
library(WGCNA)
library(clusterProfiler)
library(DEGreport)
source("FBidsTOSymbol.R")
library(RNAseqQC)
library(ensembldb)
library(dplyr)
library(ggplot2)
library(purrr)
library(tidyr)
library(tibble)
library(magrittr)
library(simplifyEnrichment)
library(stats)
library(msigdbr)
library(GO.db)
library(ggridges)
library(enrichplot)
library(ggupset)
library(gplots)
library(UpSetR)
library(rrvgo)
library(IHW)
library(patchwork)
library(openxlsx)
```

## Read count tables/group info into R.
Acquiring data from the GitHub account:
```{r data acquisition, GitHub}
cts <- as.matrix(read.csv("C:/Users/yevge/Dropbox/Brown/Work/rapa_tissue/rapa_count_table.csv", row.names = 1))
cts <- subset(cts, select = -OOFCH4) #remove OOFCH4

coldata <- read.csv("C:/Users/yevge/Dropbox/Brown/Work/rapa_tissue/rapa_group_data.csv", row.names = 1)
coldata <- coldata[colnames(cts),]

coldata$Treatment <- as.factor(coldata$Treatment)
coldata$Species <- as.factor(coldata$Species)
coldata$Sex <- as.factor(coldata$Sex)
coldata$Tissue <- as.factor(coldata$Tissue)
```

### Go annotations set up

```{r set up GO annotations}

orgDb=org.Dm.eg.db
columns(orgDb)

all_flybase_ids <- keys(orgDb, keytype = "FLYBASE")

go_annotations <- AnnotationDbi::select(orgDb, keys = all_flybase_ids, columns = c("FLYBASE", "GO"), keytype = "FLYBASE")

go_annotations <- go_annotations %>% 
  dplyr::filter(ONTOLOGY=="BP")

go_annotations <- go_annotations[, c("GO","FLYBASE")]
go_annotations <- na.omit(go_annotations)

go_annotations$TERM <- AnnotationDbi::select(GO.db, keys = go_annotations$GO, columns = "TERM", keytype = "GOID")$TERM
go_annotations <- go_annotations[, c("TERM", "FLYBASE", "GO")]

go_annotations$NAME <- paste(go_annotations$GO, go_annotations$TERM, sep=" ")
go_annotations <- go_annotations[,c("NAME","FLYBASE")]

```

## Female Heads

```{r subset count data to female heads}

cts_fh <- cts[,substring(colnames(cts), 3, 3)=="F" & substring(colnames(cts), 5, 5)=="H"] 
coldata_fh <- coldata[colnames(cts_fh),]

gene_universe_fh <- rownames(cts[rowSums(cts_fh)>0, ])
length(gene_universe_fh)

go_annotations_fh <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_fh)

ifelse(!dir.exists("results/Female_Head"), dir.create("results/Female_Head", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_fh, "results/Female_Head/gene_universe_fh.txt")

#columns of the count matrix and the rows of the column data (information about samples) must be the same so check:
all(rownames(coldata_fh) %in% colnames(cts_fh)) #all rownames of coldate match colnames of count matrix
all(rownames(coldata_fh) == colnames(cts_fh)) #are they in the same order?
```

### Rapa x Mito Interaction

```{r make a new DESeqDataSet for female heads RT interaction}
dds_fh <- DESeqDataSetFromMatrix(countData = cts_fh,
                              colData = coldata_fh,
                              design = ~ Species + Treatment + Species:Treatment) 
keep <- rowSums(counts(dds_fh)) >= 1 #minimal pre-filtering
dds_fh <- dds_fh[keep,]

dds_fh <- DESeq(dds_fh)

fhi <- results(dds_fh, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, name="SpeciesSO.TreatmentRapa", filterFun=ihw)
summary(fhi)

fhi_Ordered <- fhi[order(fhi$pvalue),]
fhi_Sig <- subset(fhi_Ordered, padj < FDR.Thresh) #1 gene
```

## Female Thorax

```{r subset count data to female thorax}

cts_ft <- cts[,substring(colnames(cts), 3, 3)=="F" & substring(colnames(cts), 5, 5)=="T"] 
coldata_ft <- coldata[colnames(cts_ft),]

gene_universe_ft <- rownames(cts[rowSums(cts_ft)>0, ])
length(gene_universe_ft)
go_annotations_ft <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_ft)

ifelse(!dir.exists("results/Female_Thorax"), dir.create("results/Female_Thorax", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_ft, "results/Female_Thorax/gene_universe_ft.txt")

#columns of the count matrix and the rows of the column data (information about samples) must be the same so check:
all(rownames(coldata_ft) %in% colnames(cts_ft)) #all rownames of coldate match colnames of count matrix
all(rownames(coldata_ft) == colnames(cts_ft)) #are they in the same order?
```

### Rapa x Mito Interaction

```{r make a new DESeqDataSet for female thorax RT interaction}
dds_ft <- DESeqDataSetFromMatrix(countData = cts_ft,
                              colData = coldata_ft,
                              design = ~ Species + Treatment + Species:Treatment) #design matrix with no intercept

keep <- rowSums(counts(dds_ft)) >= 1 #minimal pre-filtering
dds_ft <- dds_ft[keep,]
dds_ft <- DESeq(dds_ft)
resultsNames(dds_ft)
fti <- results(dds_ft, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, name="SpeciesSO.TreatmentRapa", filterFun=ihw)
summary(fti)

fti_Ordered <- fti[order(fti$pvalue),]
fti_Sig <- subset(fti_Ordered, padj < FDR.Thresh) #2 genes

```

## Female Abdomen

```{r subset count data to female abdomen}

cts_fa <- cts[,substring(colnames(cts), 3, 3)=="F" & substring(colnames(cts), 5, 5)=="A"] 
coldata_fa <- coldata[colnames(cts_fa),]

gene_universe_fa <- rownames(cts[rowSums(cts_fa)>0, ])
length(gene_universe_fa)
go_annotations_fa <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_fa)

ifelse(!dir.exists("results/Female_Abdomen"), dir.create("results/Female_Abdomen", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_fa, "results/Female_Abdomen/gene_universe_fa.txt")

#columns of the count matrix and the rows of the column data (information about samples) must be the same so check:
all(rownames(coldata_fa) %in% colnames(cts_fa)) #all rownames of coldate match colnames of count matrix
all(rownames(coldata_fa) == colnames(cts_fa)) #are they in the same order?
```


### Rapa x Mito Interaction

```{r make a new DESeqDataSet for female abdomen RT interaction}
dds_fa <- DESeqDataSetFromMatrix(countData = cts_fa,
                              colData = coldata_fa,
                              design = ~ Species + Treatment + Species:Treatment) #design matrix with no intercept

keep <- rowSums(counts(dds_fa)) >= 1 #minimal pre-filtering

dds_fa <- dds_fa[keep,]
dds_fa <- DESeq(dds_fa)
resultsNames(dds_fa)

fai <- results(dds_fa, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, name="SpeciesSO.TreatmentRapa", filterFun=ihw)
summary(fai)

fai_Ordered <- fai[order(fai$pvalue),]
fai_Sig <- subset(fai_Ordered, padj < FDR.Thresh) #2 genes
```

## Male Heads

```{r subset count data to male heads}

cts_mh <- cts[,substring(colnames(cts), 3, 3)=="M" & substring(colnames(cts), 5, 5)=="H"] 
coldata_mh <- coldata[colnames(cts_mh),]

gene_universe_mh <- rownames(cts[rowSums(cts_mh)>0, ])
length(gene_universe_mh)
go_annotations_mh <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_mh)

ifelse(!dir.exists("results/Male_Head"), dir.create("results/Male_Head", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_mh, "results/Male_Head/gene_universe_mh.txt")

#columns of the count matrix and the rows of the column data (information about samples) must be the same so check:
all(rownames(coldata_mh) %in% colnames(cts_mh)) #all rownames of coldate match colnames of count matrix
all(rownames(coldata_mh) == colnames(cts_mh)) #are they in the same order?
```


### Rapa x Mito Interaction

```{r make a new DESeqDataSet for male head RT interaction}
dds_mh <- DESeqDataSetFromMatrix(countData = cts_mh,
                              colData = coldata_mh,
                              design = ~ Species + Treatment + Species:Treatment) #design matrix with no intercept

keep <- rowSums(counts(dds_mh)) >= 1 #minimal pre-filtering

dds_mh <- dds_mh[keep,]
dds_mh <- DESeq(dds_mh)

mhi <- results(dds_mh, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, name="SpeciesSO.TreatmentRapa", filterFun=ihw)

mhi_Ordered <- mhi[order(mhi$pvalue),]
mhi_Sig <- subset(mhi_Ordered, padj < FDR.Thresh) #5 genes

GO_mhi <- simplify(enrichGO(rownames(mhi_Sig), OrgDb=drosophila2.db, universe = gene_universe_mh, keyType = "FLYBASE", ont = "BP"))

```

## Male Thorax

```{r subset count data to male thorax}

cts_mt <- cts[,substring(colnames(cts), 3, 3)=="M" & substring(colnames(cts), 5, 5)=="T"] 
coldata_mt <- coldata[colnames(cts_mt),]

gene_universe_mt <- rownames(cts[rowSums(cts_mt)>0, ])
length(gene_universe_mt)
go_annotations_mt <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_mt)

ifelse(!dir.exists("results/Male_Thorax"), dir.create("results/Male_Thorax", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_mt, "results/Male_Thorax/gene_universe_mt.txt")

#columns of the count matrix and the rows of the column data (information about samples) must be the same so check:
all(rownames(coldata_mt) %in% colnames(cts_mt)) #all rownames of coldate match colnames of count matrix
all(rownames(coldata_mt) == colnames(cts_mt)) #are they in the same order?
```


### Rapa x Mito Interaction

```{r make a new DESeqDataSet for male thorax RT interaction}
dds_mt <- DESeqDataSetFromMatrix(countData = cts_mt,
                              colData = coldata_mt,
                              design = ~ Species + Treatment + Species:Treatment) #design matrix with no intercept

keep <- rowSums(counts(dds_mt)) >= 1 #minimal pre-filtering

dds_mt <- dds_mt[keep,]
dds_mt <- DESeq(dds_mt)
resultsNames(dds_mt)
mti <- results(dds_mt, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, name="SpeciesSO.TreatmentRapa", filterFun=ihw)

mti_Ordered <- mti[order(mti$pvalue),]
mti_Sig <- subset(mti_Ordered, padj < FDR.Thresh) #0 genes
```


## Male Abdomen

```{r subset count data to male abdomen}

cts_ma <- cts[,substring(colnames(cts), 3, 3)=="M" & substring(colnames(cts), 5, 5)=="A"] 
coldata_ma <- coldata[colnames(cts_ma),]

gene_universe_ma <- rownames(cts[rowSums(cts_ma)>0, ])
length(gene_universe_ma)
go_annotations_ma <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_ma)


ifelse(!dir.exists("results/Male_Abdomen"), dir.create("results/Male_Abdomen", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_ma, "results/Male_Abdomen/gene_universe_ma.txt")

#columns of the count matrix and the rows of the column data (information about samples) must be the same so check:
all(rownames(coldata_ma) %in% colnames(cts_ma)) #all rownames of coldate match colnames of count matrix
all(rownames(coldata_ma) == colnames(cts_ma)) #are they in the same order?
```


### Rapa x Mito Interaction

```{r make a new DESeqDataSet for male abdomen RT interaction}
dds_ma <- DESeqDataSetFromMatrix(countData = cts_ma,
                              colData = coldata_ma,
                              design = ~ Species + Treatment + Species:Treatment) #design matrix with no intercept

keep <- rowSums(counts(dds_ma)) >= 1 #minimal pre-filtering

dds_ma <- dds_ma[keep,]
dds_ma <- DESeq(dds_ma)
resultsNames(dds_ma)

mai <- results(dds_ma, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, name="SpeciesSO.TreatmentRapa", filterFun=ihw)

mai_Ordered <- mai[order(mai$pvalue),]
mai_Sig <- subset(mai_Ordered, padj < FDR.Thresh) #1 gene

GO_mai <- enrichGO(rownames(mai_Sig), OrgDb=drosophila2.db, universe = gene_universe_ma, keyType = "FLYBASE", ont = "BP")
as.data.frame(GO_mai)
GO_mai_simp <- simplify(GO_mai)
barplot(GO_mai_simp, showCategory = 20, title = "Male Abdomen") 

```




## Interactions barplot

```{r}

dataframes <- list(MA=mai_Sig, FA=fai_Sig, MT=mti_Sig, FT=fti_Sig, MH=mhi_Sig, FH=fhi_Sig)

lengths <- sapply(dataframes, function(df) nrow(df))

df_lengths <- data.frame(Sample = names(dataframes), GeneCount = lengths)
df_lengths$Sex <- substring(df_lengths$Sample,1,1)
df_lengths <- df_lengths %>% 
  mutate(Sex=ifelse(Sex=="M", "Male", "Female"))
df_lengths$Tissue <- substring(df_lengths$Sample, 2,2)

df_lengths <- df_lengths %>%
  mutate(Tissue = ifelse(Tissue=="T", "Thorax", 
                         ifelse(Tissue=="A", "Abdomen", "Head")))  
df_lengths$SexTissue <- paste(df_lengths$Sex, df_lengths$Tissue, sep='\n')  

ggplot(df_lengths, aes(x = SexTissue, y = GeneCount, fill = Sex)) +
  geom_bar(stat = "identity") +
  labs(title = "Mito X Treatment Interaction Genes", x = "Sample", y = "Number of DEGs")+
  geom_text(aes(label = GeneCount), vjust = -0.5, color = "black", size = 3)

```

## Make Excel File

```{r}
dfs <- list("Male Abdomen"=as.data.frame(mai_Sig), 
            "Female Abdomen"=as.data.frame(fai_Sig),
            "Male Thorax"=as.data.frame(mti_Sig),
            "Female Thorax"=as.data.frame(fti_Sig),
            "Male Head"=as.data.frame(mhi_Sig), 
            "Female Head"=as.data.frame(fhi_Sig))

wb <- createWorkbook()

for (name in names(dfs)) {
  addWorksheet(wb, name)
  writeData(wb, sheet = name, rowNames=TRUE, x = dfs[[name]])
}

saveWorkbook(wb, "TableS10_v2.xlsx", overwrite = TRUE)
```



```{r session_info}
devtools::session_info()
```

This document was processed on: `r Sys.Date()`