---
title: "Rapa-by-Tissue Interaction Analysis"
author: "Yevgeniy Raynes"
output:
  html_document:
    toc: true
params:
   FDR: 0.05
   LFC: 0.0
date: "2023-10-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
FDR.Thresh <- params$FDR
LFC.Thresh <- params$LFC
set.seed(1234)
```


# RNAseq analysis of the impact of tissue on the reponse to Rapa


## Load packages.
This document depends on the following packages:
```{r, message=FALSE}
library(tidyverse)
library(DESeq2)
library(apeglm)
library(eulerr)
library(EnhancedVolcano)
library(flybaseR)
library(drosophila2.db)
library(org.Dm.eg.db)
library(AnnotationDbi)
library(repr)
library(vsn)
library(pheatmap)
library(WGCNA)
library(clusterProfiler)
library(DEGreport)
source("FBidsTOSymbol.R")
library(RNAseqQC)
library(ensembldb)
library(dplyr)
library(ggplot2)
library(purrr)
library(tidyr)
library(tibble)
library(magrittr)
library(simplifyEnrichment)
library(stats)
library(msigdbr)
library(GO.db)
library(ggridges)
library(enrichplot)
library(ggupset)
library(gplots)
library(UpSetR)
library(rrvgo)
library(IHW)
library(patchwork)
```

## Read count tables/group info into R.
Acquiring data 
```{r, data acquisition}
cts <- as.matrix(read.csv("C:/Users/yevge/Dropbox/Brown/Work/rapa_tissue/rapa_count_table.csv", row.names = 1)) 
coldata <- read.csv("C:/Users/yevge/Dropbox/Brown/Work/rapa_tissue/rapa_group_data.csv", row.names = 1)

cts <- subset(cts, select = -OOFCH4)
coldata <- coldata[colnames(cts),]

coldata$Species <- as.factor(coldata$Species)
coldata$Treatment <- as.factor(coldata$Treatment)
coldata$Tissue <- as.factor(coldata$Tissue)
coldata$Group <- as.factor(coldata$Group)
coldata$TissueTreatment <- paste0(coldata$Tissue, coldata$Treatment)
coldata$TissueTreatment <- as.factor(coldata$TissueTreatment)
coldata$Treatment <- relevel(coldata$Treatment, "Rapa")

```

### Go annotations set up

```{r set up GO annotations}

orgDb=org.Dm.eg.db
columns(orgDb)

all_flybase_ids <- keys(orgDb, keytype = "FLYBASE")

go_annotations <- select(orgDb, keys = all_flybase_ids, columns = c("FLYBASE", "GO"), keytype = "FLYBASE")
kegg_annotations <- select(orgDb, keys = all_flybase_ids, columns = c("FLYBASE", "PATH"), keytype = "FLYBASE")
kegg_annotations <- na.omit(kegg_annotations)

#go_annotations <-   go_annotations[go_annotations$ONTOLOGY == "BP", ]
go_annotations <- go_annotations %>% 
  dplyr::filter(ONTOLOGY=="BP")

go_annotations <- go_annotations[, c("GO","FLYBASE")]
go_annotations <- na.omit(go_annotations)

go_annotations$TERM <- select(GO.db, keys = go_annotations$GO, columns = "TERM", keytype = "GOID")$TERM
go_annotations <- go_annotations[, c("TERM", "FLYBASE", "GO")]

go_annotations$NAME <- paste(go_annotations$GO, go_annotations$TERM, sep=" ")
go_annotations <- go_annotations[,c("NAME","FLYBASE")]

```


# FEMALES

```{r subset count table to female data}
cts_f <- cts[,substring(colnames(cts), 3, 3)=="F"] #Subset the data to just columns with F
coldata_f <- coldata[colnames(cts_f),]
gene_universe_f <- rownames(cts_f[rowSums(cts_f)>0, ])
length(gene_universe_f)

ifelse(!dir.exists("results/Females"), dir.create("results/Females", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_f, "results/Females/gene_universe_f.txt")

levels(coldata_f$Tissue)

go_annotations_F <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_f)
```


## Tissue x Treatment Interaction

### DESeqDataSet: Treatment x Species x Tissue

```{r make a new dds object with female data}
dds_f <- DESeqDataSetFromMatrix(countData = cts_f,
                              colData = coldata_f,
                              design = ~ Treatment * Species * Tissue) 
keep <- rowSums(counts(dds_f)) >= 1 #minimal pre-filtering
table(keep)
dds_f <- dds_f[keep,]

dds_f <-  DESeq(dds_f)
resultsNames(dds_f)
```

### Interaction between treatment and tissue: Females

```{r treatment x tissue interactions for female data}
res_Tr_Tiss_AH_F <- results(dds_f, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh,  name="TreatmentControl.TissueHead", filterFun=ihw) 
# the interaction term for treatment effect in Abdomen vs Head 
# i.e. Abdomen - Head
summary(res_Tr_Tiss_AH_F)
res_Tr_Tiss_AH_F_Ordered <- res_Tr_Tiss_AH_F[order(res_Tr_Tiss_AH_F$pvalue),]
res_Tr_Tiss_AH_F_Sig <- subset(res_Tr_Tiss_AH_F_Ordered, padj < 0.05)

write.csv(res_Tr_Tiss_AH_F_Sig, "results/Females/Tr_Tiss_AH_F.csv")


head(convertFBids(row.names(res_Tr_Tiss_AH_F_Sig)))

res_Tr_Tiss_AT_F <- results(dds_f, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh,  name="TreatmentControl.TissueThorax", filterFun=ihw) 
# the interaction term for treatment effect in Thorax vs Abdomen
# i.e. Abdomen - Thorax
summary(res_Tr_Tiss_AT_F)
res_Tr_Tiss_AT_F_Ordered <- res_Tr_Tiss_AT_F[order(res_Tr_Tiss_AT_F$pvalue),]
res_Tr_Tiss_AT_F_Sig <- subset(res_Tr_Tiss_AT_F_Ordered, padj < 0.05)
write.csv(res_Tr_Tiss_AT_F_Sig, "results/Females/Tr_Tiss_AT_F.csv")

res_Tr_Tiss_TH_F <- results(dds_f, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh, 
                            contrast=list("TreatmentControl.TissueHead","TreatmentControl.TissueThorax"), filterFun=ihw) 
# the interaction term for treatment effect in Head vs Thorax
# i.e. Thorax - Head 
summary(res_Tr_Tiss_TH_F)
res_Tr_Tiss_TH_F_Ordered <- res_Tr_Tiss_TH_F[order(res_Tr_Tiss_TH_F$pvalue),]
res_Tr_Tiss_TH_F_Sig <- subset(res_Tr_Tiss_TH_F_Ordered, padj < 0.05)
write.csv(res_Tr_Tiss_TH_F_Sig, "results/Females/Tr_Tiss_TH_F.csv")

```



```{r, fig.height=6, fig.width=6}

a <- EnhancedVolcano(res_Tr_Tiss_AH_F,
  lab = convertFBids(rownames(res_Tr_Tiss_AH_F)),
  x = 'log2FoldChange',
  y = 'pvalue',
  title = 'Tissue x Treatment: HvA',
  legendPosition = 'bottom',
  legendLabSize = 12,
  legendIconSize = 4.0)

b <- EnhancedVolcano(res_Tr_Tiss_AT_F,
  lab = convertFBids(rownames(res_Tr_Tiss_AT_F)),
  x = 'log2FoldChange',
  y = 'pvalue',
  title = 'Tissue x Treatment: TvA',
  legendPosition = 'bottom',
  legendLabSize = 12,
  legendIconSize = 4.0)

c <- EnhancedVolcano(res_Tr_Tiss_TH_F,
  lab = convertFBids(rownames(res_Tr_Tiss_TH_F)),
  x = 'log2FoldChange',
  y = 'pvalue',
  title = 'Tissue x Treatment: HvT',
  legendPosition = 'bottom',
  legendLabSize = 12,
  legendIconSize = 4.0)
```


```{r, fig.height=10, fig.width=15}
cowplot::plot_grid(a, b, c, ncol=3)
```

### GO enrichment

#### Abd vs Head

```{r, abdomen vs head, fig.height=10, fig.width=6}
 
GO_Tr_Tiss_AH_F <- enrichGO(rownames(res_Tr_Tiss_AH_F_Sig), OrgDb=drosophila2.db, universe = gene_universe_f, keyType = "FLYBASE", ont = "BP")
GO_Tr_Tiss_AH_F_simp <- simplify(GO_Tr_Tiss_AH_F, cutoff = .7) #24 categories

write.csv(GO_Tr_Tiss_AH_F_simp, "results/Females/GO_Tr_Tiss_AH_F.csv")
```

#### Abd vs Thorax

```{r, abdomen vs thorax, fig.height=10, fig.width=6}
GO_Tr_Tiss_AT_F <- enrichGO(rownames(res_Tr_Tiss_AT_F_Sig), OrgDb=drosophila2.db, universe = gene_universe_f, keyType = "FLYBASE", ont = "BP")
GO_Tr_Tiss_AT_F_simp <- simplify(GO_Tr_Tiss_AT_F, cutoff = .7) #32 categories

write.csv(GO_Tr_Tiss_AT_F_simp, "results/Females/GO_Tr_Tiss_AT_F.csv")
```

#### Thorax vs Head

```{r, thorax v head, fig.height=10, fig.width=6}
 
GO_Tr_Tiss_TH_F <- enrichGO(rownames(res_Tr_Tiss_TH_F_Sig), OrgDb=drosophila2.db, universe = gene_universe_f, keyType = "FLYBASE", ont = "BP")
## NO ENRICHMENT
```

# MALES

```{r subset count table to male data}
cts_m <- cts[,substring(colnames(cts), 3, 3)=="M"] #Subset the data to just columns with M
coldata_m <- coldata[colnames(cts_m),]
gene_universe_m <- rownames(cts_m[rowSums(cts_m)>0, ])
length(gene_universe_m)

ifelse(!dir.exists("results/Males"), dir.create("results/Males", recursive=TRUE), print("directory already exists"))
writeLines(gene_universe_m, "results/Males/gene_universe_m.txt")

go_annotations_M <- go_annotations %>%
  dplyr::filter(FLYBASE %in% gene_universe_m)
```

## Tissue x Treatment Interaction

### DESeqDataSet: Treatment x Species x Tissue

```{r make a new dds object with male data}
dds_m <- DESeqDataSetFromMatrix(countData = cts_m,
                              colData = coldata_m,
                              design = ~ Treatment * Species * Tissue) 
keep <- rowSums(counts(dds_m)) >= 1 #minimal pre-filtering
table(keep)
dds_m <- dds_m[keep,]

dds_m <-  DESeq(dds_m)
resultsNames(dds_m)
```

### Interaction between treatment and tissue: Males

```{r treatment x tissue interactions for male data, fig.height=6, fig.width=6}
res_Tr_Tiss_AH_M <- results(dds_m, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh,  name="TreatmentControl.TissueHead", filterFun=ihw) 
# the interaction term for treatment effect in Head vs Abdomen
# i.e. is rapa effect different in head compared to abdomen
summary(res_Tr_Tiss_AH_M)
res_Tr_Tiss_AH_M_Ordered <- res_Tr_Tiss_AH_M[order(res_Tr_Tiss_AH_M$pvalue),]
res_Tr_Tiss_AH_M_Sig <- subset(res_Tr_Tiss_AH_M_Ordered, padj < 0.05)
write.csv(res_Tr_Tiss_AH_M_Sig, "results/Males/Tr_Tiss_AH_M.csv")


res_Tr_Tiss_AT_M <- results(dds_m, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh,  name="TreatmentControl.TissueThorax", filterFun=ihw) 
# the interaction term for treatment effect in Thorax vs Abdomen
# i.e. is rapa effect different in thorax compared to abdomen
summary(res_Tr_Tiss_AT_M)
res_Tr_Tiss_AT_M_Ordered <- res_Tr_Tiss_AT_M[order(res_Tr_Tiss_AT_M$pvalue),]
res_Tr_Tiss_AT_M_Sig <- subset(res_Tr_Tiss_AT_M_Ordered, padj < 0.05)
write.csv(res_Tr_Tiss_AT_M_Sig, "results/Males/Tr_Tiss_AT_M.csv")


res_Tr_Tiss_TH_M <- results(dds_m, alpha = FDR.Thresh, lfcThreshold = LFC.Thresh,  contrast=list("TreatmentControl.TissueHead","TreatmentControl.TissueThorax"), filterFun=ihw) 
# the interaction term for treatment effect in Head vs Thorax
# i.e. is rapa effect different in Head compared to Thorax
summary(res_Tr_Tiss_TH_M)
res_Tr_Tiss_TH_M_Ordered <- res_Tr_Tiss_TH_M[order(res_Tr_Tiss_TH_M$pvalue),]
res_Tr_Tiss_TH_M_Sig <- subset(res_Tr_Tiss_TH_M_Ordered, padj < 0.05)
write.csv(res_Tr_Tiss_TH_M_Sig, "results/Males/Tr_Tiss_TH_M.csv")

```

### GO enrichment

#### Abd vs Head

```{r, abdomen vs head males, fig.height=10, fig.width=6}
GO_Tr_Tiss_AH_M <- enrichGO(rownames(res_Tr_Tiss_AH_M_Sig), OrgDb=drosophila2.db, universe = gene_universe_m, keyType = "FLYBASE", ont = "BP")
GO_Tr_Tiss_AH_M_simp <- simplify(GO_Tr_Tiss_AH_M, cutoff = .7) #25 categories
write.csv(GO_Tr_Tiss_AH_M_simp, "results/Males/GO_Tr_Tiss_AH_M.csv")
```

#### Abd vs Thorax

```{r, abdomen vs thorax males, fig.height=5, fig.width=7}
GO_Tr_Tiss_AT_M <- enrichGO(rownames(res_Tr_Tiss_AT_M_Sig), OrgDb=drosophila2.db, universe = gene_universe_m, keyType = "FLYBASE", ont = "BP")
GO_Tr_Tiss_AT_M_simp <- simplify(GO_Tr_Tiss_AT_M, cutoff = .7) #6 categories
write.csv(GO_Tr_Tiss_AT_M_simp, "results/Males/GO_Tr_Tiss_AT_M.csv")
```


#### Thorax vs Head

```{r, thorax v head males, fig.height=3, fig.width=4}
GO_Tr_Tiss_TH_M <- enrichGO(rownames(res_Tr_Tiss_TH_M_Sig), OrgDb=drosophila2.db, universe = gene_universe_m, keyType = "FLYBASE", ont = "BP")
GO_Tr_Tiss_TH_M_simp <- simplify(GO_Tr_Tiss_TH_M, cutoff = .7) #4 categories
write.csv(GO_Tr_Tiss_TH_M_simp, "results/Males/GO_Tr_Tiss_TH_M.csv")
```


# RESULTS

## Tissue x Treatment Interaction

### Counts

### Intersections

```{r, fig.width=8}
tissue_treatment_interaction <- list(Head.Abdomen.Females=rownames(res_Tr_Tiss_AH_F_Sig), 
                   Thorax.Abdomen.Females=rownames(res_Tr_Tiss_AT_F_Sig), 
                   Head.Thorax.Females=rownames(res_Tr_Tiss_TH_F_Sig),
                   Head.Abdomen.Males=rownames(res_Tr_Tiss_AH_M_Sig), 
                   Thorax.Abdomen.Males=rownames(res_Tr_Tiss_AT_M_Sig), 
                   Head.Thorax.Males=rownames(res_Tr_Tiss_TH_M_Sig)
                   )

names(tissue_treatment_interaction)


tissue_treatment_interaction_GO <- list(Head.Abdomen.Females=as.data.frame(GO_Tr_Tiss_AH_F_simp)$ID, 
                   Thorax.Abdomen.Females=as.data.frame(GO_Tr_Tiss_AT_F_simp)$ID, 
                   Head.Thorax.Females=as.data.frame(GO_Tr_Tiss_TH_F)$ID,
                   Head.Abdomen.Males=as.data.frame(GO_Tr_Tiss_AH_M_simp)$ID, 
                   Thorax.Abdomen.Males=as.data.frame(GO_Tr_Tiss_AT_M_simp)$ID, 
                   Head.Thorax.Males=as.data.frame(GO_Tr_Tiss_TH_M_simp)$ID
                   )

names(tissue_treatment_interaction_GO)
```

#### Upset plot

```{r, DEGs, fig.width=8}
pdf(file="degs_intersection_upset_TR_TISS.pdf",
    width = 8.1,
    height = 4,
    onefile=FALSE)
upset(
                                fromList(tissue_treatment_interaction),
                                nsets=6, 
                                sets=c("Head.Abdomen.Females",
                                       "Thorax.Abdomen.Females",
                                       "Head.Thorax.Females",
                                       "Head.Abdomen.Males",
                                       "Thorax.Abdomen.Males",
                                       "Head.Thorax.Males"),
                                order.by = c("degree"),
                                decreasing=F,
                                sets.x.label = "Total DE Gene #",
                                main.bar.color = "#984ea3", 
                                sets.bar.color = "#ff7f00",
                                matrix.color = "#984ea3",
                                att.color = "black",
                                text.scale = 1.4,
                                set_size.scale_max = 1040,
                                point.size = 2.8,
                                set_size.show=TRUE, keep.order=TRUE,
                                intersections = list(
                                  list("Head.Abdomen.Females"),
                                  list("Thorax.Abdomen.Females"),
                                  list("Head.Thorax.Females"),
                                    
                                  list("Head.Abdomen.Females", "Thorax.Abdomen.Females"),
                                  list("Head.Abdomen.Females", "Head.Thorax.Females"),
                                  list("Thorax.Abdomen.Females", "Head.Thorax.Females"),
                                  list("Head.Abdomen.Males"),
                                  list("Thorax.Abdomen.Males"),
                                  list("Head.Thorax.Males"),
                                    
                                  list("Head.Abdomen.Males", "Thorax.Abdomen.Males"),
                                  list("Head.Abdomen.Males", "Head.Thorax.Males"),
                                  list("Thorax.Abdomen.Males", "Head.Thorax.Males"),
                                  list("Head.Abdomen.Males","Head.Abdomen.Females"),
                                  list("Thorax.Abdomen.Males","Thorax.Abdomen.Females"),
                                  list("Head.Thorax.Males", "Head.Thorax.Females"),
                                  list("Head.Abdomen.Females", "Thorax.Abdomen.Females", "Head.Thorax.Females"),
                                  list("Head.Abdomen.Males", "Thorax.Abdomen.Males", "Head.Thorax.Males")
                                )
)

dev.off()
```


```{r, GO cats, fig.width=8}
pdf(file="GO_cats_intersection_upset_TR_TISS.pdf",
    width = 8.1,
    height = 4,
    onefile=FALSE)
upset(
                                fromList(tissue_treatment_interaction_GO),
                                nsets=6, 
                                sets=c("Head.Abdomen.Females",
                                       "Thorax.Abdomen.Females",
                                       "Head.Thorax.Females",
                                       "Head.Abdomen.Males",
                                       "Thorax.Abdomen.Males",
                                       "Head.Thorax.Males"),
                                order.by = c("degree"),
                                decreasing=F,
                                sets.x.label = "Total DE Gene #",
                                main.bar.color = "#984ea3", 
                                sets.bar.color = "#ff7f00",
                                matrix.color = "#984ea3",
                                att.color = "black",
                                text.scale = 1.4,
                                set_size.scale_max = 55,
                                point.size = 2.8,
                                set_size.show=TRUE, keep.order=TRUE,
                                intersections = list(
                                  list("Head.Abdomen.Females"),
                                  list("Thorax.Abdomen.Females"),
                                  list("Head.Thorax.Females"),
                                    
                                  list("Head.Abdomen.Females", "Thorax.Abdomen.Females"),
                                  list("Head.Abdomen.Females", "Head.Thorax.Females"),
                                  list("Thorax.Abdomen.Females", "Head.Thorax.Females"),
                                  list("Head.Abdomen.Males"),
                                  list("Thorax.Abdomen.Males"),
                                  list("Head.Thorax.Males"),
                                    
                                  list("Head.Abdomen.Males", "Thorax.Abdomen.Males"),
                                  list("Head.Abdomen.Males", "Head.Thorax.Males"),
                                  list("Thorax.Abdomen.Males", "Head.Thorax.Males"),
                                  list("Head.Abdomen.Males","Head.Abdomen.Females"),
                                  list("Thorax.Abdomen.Males","Thorax.Abdomen.Females"),
                                  list("Head.Thorax.Males", "Head.Thorax.Females"),
                                  list("Head.Abdomen.Females", "Thorax.Abdomen.Females", "Head.Thorax.Females"),
                                  list("Head.Abdomen.Males", "Thorax.Abdomen.Males", "Head.Thorax.Males")
                                )
)

dev.off()
```

### GO Enrichment 

```{r, fig.height=30, fig.width=18}
colors <- c(low = '#e41a1c', mid ="#984ea3", high = '#377eb8')

AH_F_GO_plot <- as.data.frame(GO_Tr_Tiss_AH_F_simp) %>% #25 cats
  arrange(p.adjust) %>%
  slice_min(p.adjust, n = 15) %>%
  mutate(Descr = str_wrap(Description, width = 35)) %>%
  ggplot(aes(fct_reorder(Descr, -p.adjust), Count, fill = p.adjust)) +
  geom_bar(stat = 'identity', color = 'black', width = 0.8) +  # Set bar color and width
  scale_fill_gradient(low = colors["low"],  high = colors["high"]) +
  ylab('DEG Count') +
  coord_flip() +
  guides(fill = guide_colorbar(title = "FDR")) + 
  theme_minimal() +  # Use minimal theme
  theme(
    legend.position = "left",
    legend.key.size = unit(1, "cm"),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 28),  # Increase font size for x-axis
    axis.text.y = element_text(size = 32),  # Increase font size for y-axis
    axis.title.x = element_text(size = 32),  # Increase font size for y-axis title
    # plot.title = element_text(size = 22),  # Increase font size for plot title
    legend.text = element_text(size = 26),  # Increase font size for legend text
    legend.title = element_text(size = 30)
  ) 


AH_M_GO_plot <- as.data.frame(GO_Tr_Tiss_AH_M_simp) %>% #48 cats
  arrange(p.adjust) %>%
  slice_min(p.adjust, n = 15) %>%
  mutate(Descr = str_wrap(Description, width = 35)) %>%
  ggplot(aes(fct_reorder(Descr, -p.adjust), Count, fill = p.adjust)) +
  geom_bar(stat = 'identity', color = 'black', width = 0.8) +  # Set bar color and width
  scale_fill_gradient(low = colors["low"],  high = colors["high"]) +
  ylab('DEG Count') +
  coord_flip() +
  guides(fill = guide_colorbar(title = "FDR")) + 
  theme_minimal() +  # Use minimal theme
  theme(
    legend.position = "right",
    legend.key.size = unit(1, "cm"),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 28),  # Increase font size for x-axis
    axis.text.y = element_text(size = 32),  # Increase font size for y-axis
    axis.title.x = element_text(size = 32),  # Increase font size for y-axis title
    # plot.title = element_text(size = 22),  # Increase font size for plot title
    legend.text = element_text(size = 26),  # Increase font size for legend text
    legend.title = element_text(size = 30)
  ) 


AT_F_GO_plot <- as.data.frame(GO_Tr_Tiss_AT_F_simp) %>% #25 cats
  arrange(p.adjust) %>%
  slice_min(p.adjust, n = 15) %>% 
  dplyr::filter(Description != "purine nucleoside monophosphate metabolic process")%>% 
  mutate(Descr = str_wrap(Description, width = 35)) %>%
  ggplot(aes(fct_reorder(Descr, -p.adjust), Count, fill = p.adjust)) +
  geom_bar(stat = 'identity', color = 'black', width = 0.8) +  # Set bar color and width
  scale_fill_gradient(low = colors["low"],  high = colors["high"]) +
  ylab('DEG Count') +
  coord_flip() +
  guides(fill = guide_colorbar(title = "FDR")) + 
  theme_minimal() +  # Use minimal theme
  theme(
    legend.position = "left",
    legend.key.size = unit(1, "cm"),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 28),  # Increase font size for x-axis
    axis.text.y = element_text(size = 32),  # Increase font size for y-axis
    axis.title.x = element_text(size = 32),  # Increase font size for y-axis title
    # plot.title = element_text(size = 22),  # Increase font size for plot title
    legend.text = element_text(size = 26),  # Increase font size for legend text
    legend.title = element_text(size = 30)
  ) 


AT_M_GO_plot <- as.data.frame(GO_Tr_Tiss_AT_M_simp) %>% #6 cats
  arrange(p.adjust) %>%
  slice_min(p.adjust, n = 6) %>%
  mutate(Descr = str_wrap(Description, width = 35)) %>%
  ggplot(aes(fct_reorder(Descr, -p.adjust), Count, fill = p.adjust)) +
  geom_bar(stat = 'identity', color = 'black', width = 0.8) +  # Set bar color and width
  scale_fill_gradient(low = colors["low"],  high = colors["high"]) +
  ylab('DEG Count') +
  coord_flip() +
  guides(fill = guide_colorbar(title = "FDR")) + 
  theme_minimal() +  # Use minimal theme
  theme(
    legend.position = "right",
    legend.key.size = unit(1, "cm"),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 28),  # Increase font size for x-axis
    axis.text.y = element_text(size = 32),  # Increase font size for y-axis
    axis.title.x = element_text(size = 32),  # Increase font size for y-axis title
    # plot.title = element_text(size = 22),  # Increase font size for plot title
    legend.text = element_text(size = 26),  # Increase font size for legend text
    legend.title = element_text(size = 30)
  ) 


TH_M_GO_plot <- as.data.frame(GO_Tr_Tiss_TH_M_simp) %>% #4 cats
  arrange(p.adjust) %>%
  slice_min(p.adjust, n = 4) %>%
  mutate(Descr = str_wrap(Description, width = 35)) %>%
  ggplot(aes(fct_reorder(Descr, -p.adjust), Count, fill = p.adjust)) +
  geom_bar(stat = 'identity', color = 'black', width = 0.8) +  # Set bar color and width
  scale_fill_gradient(low = colors["low"],  high = colors["high"]) +
  ylab('DEG Count') +
  coord_flip() +
  guides(fill = guide_colorbar(title = "FDR")) + 
  theme_minimal() +  # Use minimal theme
  theme(
    legend.position = "right",
    legend.key.size = unit(1, "cm"),
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 28),  # Increase font size for x-axis
    axis.text.y = element_text(size = 32),  # Increase font size for y-axis
    axis.title.x = element_text(size = 32),  # Increase font size for y-axis title
    # plot.title = element_text(size = 22),  # Increase font size for plot title
    legend.text = element_text(size = 26),  # Increase font size for legend text
    legend.title = element_text(size = 30)
  ) 

```


```{r, fig.height=30, fig.width=18}
AT_TH <- wrap_elements(grid::textGrob('Test')) + AT_M_GO_plot + grid::textGrob('Test') + TH_M_GO_plot + grid::textGrob('Test') + plot_layout(ncol = 1, heights = c(2, 6, 2, 4, 1))

go_enrichment_plot <- AH_F_GO_plot + AT_F_GO_plot + AH_M_GO_plot + AT_TH + plot_layout(ncol = 2, byrow = FALSE)

ggsave("TissueTreatment_GO_Enrich.pdf", plot = go_enrichment_plot, width = 30, height = 34, dpi = 300)
```


```{r session_info}
devtools::session_info()
```

This document was processed on: `r Sys.Date()`